\resumeSubHeadingListStart
\resumeSubheading{Zscaler}{}{AI Platform Innovation Intern}{Jun 2025 -- Oct 2025}
\resumeItemListStart
  \resumeItem{Recognized inefficiencies in migrating data to Zscaler's internal AI knowledgebase and spearheaded the design and launch of a full-stack Python web app (now in production), saving 125 hours of manual work for the company.}
  \resumeItem{Developed a Python tool that benchmarks AI resume evaluations against human references, producing detailed accuracy reports to enable scalable diagnostics and model refinement. This is forecasted to save 60 company hours annually. Model accuracy improved 35\%.}
  \resumeItem{Built and deployed a secure Python REST API that lets Zapier AI automations read/update/append Google Sheets in our private cloud, bypassing the fixed row limit and replacing per-row fees with a flat 1¢ per run — now live and saving Zscaler hundreds of dollars per week.}
\resumeItemListEnd

\resumeSubheading{Polycade}{}{Software Engineering Intern}{Jul 2024 -- Sep 2024}
\resumeItemListStart
  \resumeItem{Engineered a Python RAG-enabled GenAI chatbot which provides niche product info, clickable links, and brand-specific style/tone to streamline customer support.}
  \resumeItem{Implemented a Python web scraper to extract company info for vectorstore ingestion by parsing HTML/CSS content into clean Markdown for pages within the Polycade sitemap.}
  \resumeItem{Containerized and deployed a custom shell script using Docker, enabling Google Sheets automation to simplify data ingestion.}
  \resumeItem{Bolstered RAG's functionality by designing an algorithm that allows my agent to reason and query for itself.}
\resumeItemListEnd

\resumeSubheading{RRS Solutions}{}{Artificial Intelligence Software Intern}{Mar 2024 -- Aug 2024}
\resumeItemListStart
  \resumeItem{Designed a caching system to prevent redundant API calls, lowering the cost of an internal process by 94.2\%.}
  \resumeItem{Developed a robust and scalable data ingestion pipeline (for multiple document file types) with Python, harnessing LangChain and a local embedding model to populate a ChromaDB vectorstore.}
\resumeItemListEnd
\resumeSubHeadingListEnd
