\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{ReadySetRead} $|$ \emph{Independent}}{}
    \resumeItemListStart
      \resumeItem{Desc here}
    \resumeItemListEnd

  \resumeProjectHeading{\textbf{Vehicle Recognition Platform} $|$ \emph{Independent}}{}
    \resumeItemListStart
      \resumeItem{Designed and deployed a multimodal vehicle recognition service using Gemini, Docker, and Google Cloud Run.}
      \resumeItem{Engineered a specialized backend for vehicle research and retrieval, delivering higher accuracy and more relevant info than Google Lens.}
    \resumeItemListEnd

  \resumeProjectHeading{\textbf{Deep Learning for Ultrasound Imaging (webpages.scu.edu/ftp/jbouret)} $|$ \emph{Maternal Health Foundation}}{}
    \resumeItemListStart
      \resumeItem{Served as team lead \& codebase admin for my team's Python-based Deep Learning project, managing version control \& code integrity.}
      \resumeItem{Developed software to predict and prevent childbirth complications in underserved countries, under Dr. Shayganfar's guidance.}
    \resumeItemListEnd

  \resumeProjectHeading{\textbf{Social Network App Concept} $|$ \emph{Independent}}{}
    \resumeItemListStart
	\resumeItem{Developed from scratch using C++ with Qt Creator.}
	\resumeItem{Implemented a clickable GUI, public/private messaging, a friend suggestion algorithm, and a dynamic back button.}
	\resumeItem{Employed several handmade graph algorithms for network analysis and visualization.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
